\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-05-02 journalSwarmControl/theory.tex
Edited some texts

\begin{algorithm}
\caption{Hybrid mean and variance control}\label{alg:MeanVarianceControl}
\begin{algorithmic}[1]
\Require Knowledge of swarm mean $[\bar{x},\bar{y}]$, variance $[\sigma_x^2, \sigma_y^2]$, the locations of the rectangular boundary $\{x_{min}, x_{max}, y_{min}, y_{max}\}$, and the target mean position $[x_{\rm{target}},y_{\rm{target}}]$.%TODO: use  \AND, \OR, \XOR, \NOT, \TO, \TRUE, \FALSE \gets
\State $x_{goal} \gets  x_{\rm{target}}$, $y_{\rm{goal}} \gets y_{\rm{target}}$
\Loop
%\State  Compute $\sigma_x^2, \sigma_y^2$

>>>>

\begin{algorithm}
\caption{Hybrid mean and variance control}\label{alg:MeanVarianceControl}
\begin{algorithmic}[1]
\Require Knowledge of swarm mean $[\bar{x},\bar{y}]$, variance $[\sigma_x^2, \sigma_y^2]$, the locations of the rectangular boundary $\{x_{\rm{min}}, x_{\rm{max}}, y_{\rm{min}}, y_{\rm{max}}\}$, and the target mean position $[x_{\rm{target}},y_{\rm{target}}]$.%TODO: use  \AND, \OR, \XOR, \NOT, \TO, \TRUE, \FALSE \gets
\State $x_{goal} \gets  x_{\rm{target}}$, $y_{\rm{goal}} \gets y_{\rm{target}}$
\Loop
%\State  Compute $\sigma_x^2, \sigma_y^2$
